Report

### 2014-11-21 MSLLReport.tex
add ppts about maxent models

\documentclass[slidestop,compress,mathserif]{beamer}
\usepackage{setspace}
\usepackage{ragged2e}
\usepackage{biblatex}
\bibliography{Domingos}
\let\raggedright=\RaggedRight
%\usepackage[bars]{beamerthemetree} % Beamer theme v 2.2
\usetheme{Antibes} % Beamer theme v 3.0
\usecolortheme{lily} % Beamer color theme
\title{Report}
\author{Cuiyi}
\institute{}

@@

	\begin{frame}
		\frametitle{Maximum Entropy Models}
		\textbf{The principle of maximum entropy states} that, subject to precisely stated prior data, the model which best represents the current state of knowledge is one with largest entropy.
		Given a sample collection, $$\mathcal{T}=\{(x_1,y_1),(x_2,y_2),\ldots,(x_N,y_N)\}$$
		Where $\mathcal{X}=\{x_1,\ldots,x_N\}$ is input set, $\mathcal{Y}=\{y_1,\ldots,y_N\}$ is output set. Our goal is to chose a best classifier which can output $y$ according to probability distribution $p(y|x)$.

@@

	\begin{frame}
		\frametitle{Maximum Entropy Models(2)}
		Here, we use binary feature function for feature selection.
		$$f(x,y)=\left\{
		\begin{array}{ll}
		1  &\mbox{if $x,y$ satisfy some condition}\\
		0  &\mbox{otherwise}
		\end{array}
		\right.
		$$
		In statistics, the empirical distribution is the cumulative distribution associated with the empirical measure of the sample.

		Let $\hat{p}(x,y)$ and $\hat{p}(x)$ to be defined as:
		$$\hat{p}(x,y) = \frac{count(x,y)}{N},\hat{p}(x) = \frac{count(x)}{N}$$
	\end{frame}
	\section{Distance and Divergence}
	\begin{frame}
		\frametitle{Distance}
		\textbf{Distance} satisfies four constraints which \text{Divergence} may no satisfy.
		\begin{itemize}
			\item \textbf{Non-negativity:} $\forall x,y,\quad d(x,y) \ge 0$
			\item \textbf{Non-degeneracy:} $d(x,y)=0 \Leftrightarrow x=y$
			\item \textbf{Symmetry:} $\forall x,y, \quad d(x,y)=d(y,x)$
			\item \textbf{Triangularity:} $\forall x,y,z \quad d(x,z)\leq d(x,y)+d(y,z)$
		\end{itemize}
		\begin{figure}
			\pgfimage[width=4cm]{"image/29.png"}
		\end{figure}	
	\end{frame}

@@

	\begin{frame}
		\frametitle{Distance(3)}
		\textbf{Why is Euclidean distance not a good metric in high dimensions?}
		\begin{itemize}
			\item 
		\end{itemize}
		Here is text
		\fullcite{Domingos}

	\end{frame}
\end{document}

>>>>

\documentclass[slidestop,compress,mathserif]{beamer}
\usepackage{setspace}
\usepackage{ragged2e}
\usepackage{biblatex}
\usepackage{algorithm}           
\usepackage{algorithmic}
\bibliography{Domingos}
\let\raggedright=\RaggedRight
%\usepackage[bars]{beamerthemetree} % Beamer theme v 2.2
\usetheme{Antibes} % Beamer theme v 3.0
\usecolortheme{lily} % Beamer color theme
\title{Report}
\author{Cuiyi}
\institute{}

@@

	\begin{frame}[shrink]
		\frametitle{Motivating example}
		Suppose we want a model translate English word \textit{in} to French.

		Let $p$ denote the model, and $p(f)$ denote the probability that $f$ is chose as a translation of \textit{in}.($f \in \{\mbox{dans,en,\`{a},au cours de,pendant}\}$)

		Now, we can impose our first constraint on our model $p$:
		$$p(\mbox{dans})+p(\mbox{en})+p(\mbox{\`a})+p(\mbox{au cours de})+p(\mbox{pendant}) = 1$$
		With no empirical justification, the most in intuitively model is
		$$p(\mbox{dans})=p(\mbox{en})=p(\mbox{\`a})=p(\mbox{au cours de})=p(\mbox{pendant})=\frac{1}{5}$$
		If we add an additional constraint
		$$p(\mbox{dans})+p(\mbox{en}) = \frac{1}{3}$$
		subject to the constraints
		$$p(\mbox{dans})=p(\mbox{en})=\frac{3}{20};p(\mbox{\`a})=p(\mbox{au cours de})=p(\mbox{pendant})=\frac{7}{30} $$

@@

	\begin{frame}
		\frametitle{Training data}
		Let's do some form formalization, suppose we have collected a large number of samples $\{(x_1,y_1),(x_2,y_2),\ldots,(x_N,y_N)\}$.
		\newline
		\newline
		In the example we have been considering, each sample would consist of a phrase $x$ containing the words surrounding \textit{in}, together with the translation $y$ of \textit{in}.
		\newline
		\newline
		We can summarize the training example in terms of its \textbf{empirical probability distribution} $\widetilde{p}$,define by
		$$\widetilde{p}(x,y) = \frac{1}{N} \times \mbox{number of times that $(x,y)$ occurs in sample}$$
	\end{frame}

	\begin{frame}
		\frametitle{Features and constraints}
		First, let's consider the definition of \textbf{feature function}
		$$f(x,y)=\left\{
		\begin{array}{ll}
		1  &\mbox{if $x,y$ satisfy some condition}\\
		0  &\mbox{otherwise}
		\end{array}
		\right.
		$$
		In our example we have employed some constraints, but we could also consider statistics which depend on $x$.

		For instance, we might notice that, in the training example, if \textit{April} is the word following \textit{in}, then the translation of in is en with frequency $\frac{9}{10}$.

		Now we can use feature function to express the event that \textit{in} translates as \textit{en} when \textit{April} is the following word.
		$$f(x,y)=\left\{
		\begin{array}{ll}
		1  &\mbox{if $y=en$ and \textit{April} follows \textit{in}}\\
		0  &\mbox{otherwise}
		\end{array}
		\right.
		$$
	\end{frame}

	\begin{frame}
		\frametitle{Features and constraints(2)}
		The expected value of $f$ with respect to the empirical distribution $\widetilde{p}(x,y)$
		\begin{equation}
			\widetilde{p}(f) = \sum_{x,y}\widetilde{p}(x,y)f(x,y)
		\end{equation}
		The expected value of $f$ with respect to real distribution $p(x,y)$
		\begin{equation*}
			p(f) = \sum_{x,y}p(x,y)f(x,y) = \sum_{x,y}p(x)p(y|x)f(x,y)
		\end{equation*}
		For convenience, we usually use $\widetilde{p}(x)$ instead of $p(x)$
		\begin{equation}
		p(f) = \sum_{x,y}\widetilde{p}(x)p(y|x)f(x,y)
		\end{equation}
	\end{frame}

	\begin{frame}
		\frametitle{Features and constraints(3)}
		We constrain this expected value to be the same as the expected value of f in the training sample. That is, we require
		\begin{equation}
			p(f) = \widetilde{p}(f). 
		\end{equation}
		Combining (8), (9) and (10), we obtain
		\begin{equation}
			\sum_{x,y}\widetilde{p}(x)p(y|x)f(x,y) = \sum_{x,y}\widetilde{p}(x,y)f(x,y).
		\end{equation}
		We call the requirement (11) a \textbf{constraint equation} or simply a \textbf{constraint}.
	\end{frame}

	\begin{frame}
		\frametitle{The Maximum Entropy Principle}
		Suppose that we are given $n$ feature function $\{f_1,\ldots,f_n\}$, which determine statistics we feel are import in modeling the process.

		We would like our model to accord with these conditions. That is, we would like $p$ to lie in the subset $\mathcal{C}$ of $\mathcal{P}$ defined by
		\begin{equation}
			\mathcal{C} = \left\{ p\in\mathcal{P} | p(f_i) = \widetilde{p}(f_i) \quad i\in \{1,2,\ldots,n\} \right\}
		\end{equation}
		\begin{figure}
			\pgfimage[width=6cm ]{"image/31.png"}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{The Maximum Entropy Principle(2)}
		Among the models $p\in \mathcal{C}$, the maximum entropy philosophy dictates that we select the distribution which is most uniform, which means we choose $p$ maximizing the entropy
		\begin{equation}
			H(p) = -\sum_{x,y}\widetilde{p}(x,y)p(y|x)\log p(y|x)
		\end{equation}
		With these definition in hand, we can present the principle of maximum entropy
		\begin{equation}
			p^* = \mathrm{arg}\max_{p\in \mathcal{C}} H(p)
		\end{equation} 
		It can be shown that $p^*$ is well defined; that is, there is always a unique model $p^*$ with maximum entropy in any constrained set $\mathcal{C}$ 
	\end{frame}

	\begin{frame}
		\frametitle{Optimization problem}
		The constrained optimization problem at hand is to find
		\begin{equation}
			p^* = \mathrm{arg}\max_{p\in\mathcal{C}}\left(-\sum_{x,y}\widetilde{p}(x)p(y|x)\log p(y|x) \right)
		\end{equation}
		subject to
		\begin{eqnarray}
			&& p(y|x) \geq 0 \quad \mbox{for all $x,y$}\\
			&& \sum_y p(y|x) = 1 \quad \mbox{for all $x$}\\
			&& \widetilde{p}(f_i) = p(f_i) \quad \mbox{for $i\in \{1,2,\ldots,n\}$}
		\end{eqnarray}
	\end{frame}

	\begin{frame}
		\frametitle{Optimization problem(2)}
		To solve this optimization problem, introduce the Lagrangian
		\begin{equation}
			\mathcal{L}(p,\Lambda) = -H(p) + \lambda_0\left(1-\sum_y p(y|x) \right) + \sum_{i=1}^{n}\lambda_i\left(\widetilde{p}(f_i)-p(f_i)\right),
		\end{equation}
		where $\Lambda = \{\lambda_0,\lambda_1,\ldots,\lambda_n\}$.

		Then we obtain the \textbf{primary problem}
		\begin{equation}
			\min_{p\in\mathcal{C}}\max_{\Lambda}\mathcal{L}(p,\Lambda)
		\end{equation}
		For $-H(p)$ is convex function, the primary problem is equivalent to
		its \textbf{dual problem}
		\begin{equation}
			\max_{\Lambda}\min_{p\in\mathcal{C}}\mathcal{L}(p,\Lambda)
		\end{equation}
	\end{frame}

	\begin{frame}
		\frametitle{Exponential form}
		Consider the minimum problem in dual problem:
		\begin{equation}
			\Psi(\Lambda) = \min_{p\in\mathcal{C}}\mathcal{L}(p,\Lambda) = \mathcal{L}(p_\Lambda,\Lambda),
		\end{equation}
		where
		\begin{equation}
			p_\Lambda = \mathrm{arg}\max_{p\in\mathcal{C}}\Lambda(p,\Lambda).
		\end{equation}

	\begin{frame}
		\frametitle{Exponential form(2)}
		The we use \textbf{Lagrangian multiplier method} to obtain $p_\Lambda$
		\begin{eqnarray*}
			&&\frac{\partial\mathcal{L}(p,\Lambda)}{\partial p(y|x)} \\
			&=& \sum_{x,y}\widetilde{p}(x)(\log p(y|x) +1) - \sum_y\lambda_0 - \sum_{i=1}^{n}\left(\sum_{x,y}\widetilde{p}(x)f_i(x,y)\right)\\
			&=& \sum_{x,y}\widetilde{p}(x)(\log p(y|x) +1) - \sum_x\widetilde{p}(x)\sum_y\lambda_0 - \sum_{x,y}\widetilde{p}(x)\sum_{i=1}^{n}\lambda_i f_i(x,y)\\
			&=& \sum_{x,y}\widetilde{p}(x)(\log p(y|x) +1) - \sum_{x,y}\widetilde{p}(x)\lambda_0 - \sum_{x,y}\widetilde{p}(x)\sum_{i=1}^{n}\lambda_i f_i(x,y)\\
			&=& \sum_{x,y}\left(\log p(y|x) +1 -\lambda_0 -\sum_{i=1}^{n}\lambda_i f_i(x,y) \right)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}
		\frametitle{Exponential form(3)}
		Let $\frac{\partial\mathcal{L}(p,\Lambda)}{\partial p(y|x)}$ be zero, we obtain
		\begin{equation}
			\log p(y|x) +1 -\lambda_0 -\sum_{i=1}^{n}\lambda_i f_i(x,y) = 0,
		\end{equation}
		then
		\begin{equation}
			p(y|x) = e^{\lambda_0-1}\cdot e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}.
		\end{equation}
		According to constraint (17), we obtain
		\begin{equation}
			p_\Lambda = \frac{1}{Z_\Lambda(x)}e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}
		\end{equation}
		where
		\begin{equation}
			Z_\Lambda(x) = \sum_y e^{\sum_{i=1}^{n}\lambda_i f_i(x,y)}
		\end{equation}
	\end{frame}

	\begin{frame}[shrink]
		\frametitle{Maximum likelihood}
		Consider the maximum problem in dual problem:
		\begin{equation}
			\max_\Lambda \Psi(\Lambda)
		\end{equation}
		We suppose
		\begin{equation}
			\Lambda^* = \mathrm{arg}\max_\Lambda \Psi(\Lambda),
		\end{equation}
		then we can solve the optimization problem by $p^* = p_\Lambda$.

		We know
		\begin{eqnarray*}
			\Psi(\Lambda) &=& \mathcal{L}(p_\Lambda,\Lambda)\\
			&=&\sum_{x,y}\widetilde{p}(x)p_\Lambda(y|x)\log p_\Lambda(y|x) \\
			&+& \sum_{i=1}^{n}\lambda_i\left(\widetilde{p}(f_i) - \sum_{x,y}\widetilde{p}(x)p_\Lambda(y|x)f_i(x,y)\right)\\
			&=& \sum_{i=1}^{n} \lambda_i\widetilde{p}(f_i) +\sum_{x,y}\widetilde{p}(x)p_\Lambda(y|x)\left(\log p_\Lambda(y|x) - \sum_{i=1}^{n}\lambda_if_i(x,y)\right)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}
		\frametitle{Maximum likelihood (2)}
		According to (26), we obtain
		\begin{equation}
			\log p_\Lambda(y|x) = \sum_{i=1}^{n}\lambda_i f_i(x,y) - \log Z_\Lambda(x)
		\end{equation}
		substitute it to $\Psi(\Lambda)$,
		\begin{eqnarray*}
			\Psi(\Lambda) &=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i)-\sum_{x,y}\widetilde{p}(x)p_\Lambda(y|x)\log Z_\Lambda(x) \\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x \widetilde{p}(x)\log Z_\Lambda(x)\sum_y p_\Lambda(y|x)\\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\log Z_\Lambda(x)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}[shrink]
		\frametitle{Maximum likelihood (3)}
		Consider MLE:
		\begin{equation}
			\mathcal{L}_{\widetilde{p}}(p) = \log \prod_{x,y} p(y|x)^{\widetilde{p}(x,y)} = \sum_{x,y}\widetilde{p}(x,y)\log p(y|x)
		\end{equation}
		According (30) we obtain,
		\begin{eqnarray*}
			\mathcal{L}_{\widetilde{p}}(p_\Lambda) &=& \sum_{x,y}\widetilde{p}(x,y)\left(\sum_{i=1}^{n} \lambda_if_i(x,y) - \log Z_\Lambda(x) \right)\\
			&=& \sum_{x,y}\widetilde{p}(x,y)\sum_{i=1}^{n}\lambda_if_i(x,y)-\sum_{x,y}\widetilde{p}(x,y)\log Z_\Lambda(x) \\
			&=& \sum_{i=1}^{n}\lambda_i\left(\sum_{x,y}\widetilde{p}(x,y)f_i(x,y)\right) - \sum_{x,y}\widetilde{p}(x,y)\log Z_\Lambda(x)\\
			&=& \sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\log Z_\Lambda(x)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}
		\frametitle{Computing the Parameters}
		Some Parameters Optimization method in common use like\textbf{ Gradient descent}:
		\begin{eqnarray*}
			\frac{\partial\Psi}{\partial\lambda_i} &=& \frac{\partial}{\partial\lambda_i}\left(\sum_{i=1}^{n}\lambda_i\widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\log Z_{\Lambda}(x) \right)\\
			&=& \widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\frac{1}{Z_{\Lambda}(x)}\frac{\partial}{\partial\lambda_i}\left(\sum_y e^{\sum_{i=1}^{n}\lambda_if_i(x,y)} \right)\\
			&=& \widetilde{p}(f_i) - \sum_x\widetilde{p}(x)\frac{1}{Z_{\Lambda}(x)}\sum_y e^{\sum_{i=1}^{n}\lambda_if_i(x,y)}f_i(x,y)\\
			&=& \widetilde{p}(x) - \sum_x \widetilde{p}(x)\sum_y p_{\Lambda}(y|x)f_i(x,y)
		\end{eqnarray*}
	\end{frame}

	\begin{frame}
		\frametitle{GIS algorithm}
		\begin{itemize}
			\item[Step1] Initial parameters. set $\Lambda = 0$
			\item[Step2] Calculate $E_{\widetilde{p}(f_i)} = \sum_{i=1}^{n}\widetilde{p}(x,y)f_i(x,y)$, for $i=1,2,\ldots,n.$
			\item[Step3] Iteration, update parameters:
			\begin{itemize}
				\item[] Calculate $E_{p_{\Lambda}}(f_i)$, $i=1,2,\ldots,n$.
				\item[] \textbf{FOR} $i=1,2,\ldots,n$ \textbf{DO}
				\item[] \{
				\item[] $\lambda_i := \lambda_i + \eta\log\frac{E_{\widetilde{p}}(f_i)}{E_{p_{\Lambda}}(f_i)}$
				\item[] \}
			\end{itemize}
			\item[Step4] Check convergence.
		\end{itemize} 	
	\end{frame}

	\begin{frame}
		\frametitle{IIS algorithm}
		\begin{itemize}
			\item[Step1] Initial parameters, set $\Lambda := 0$
			\item[Step2] Iteration, update parameters:
			\begin{itemize}
				\item[] \textbf{FOR} $i=1,2,\ldots,n$ \textbf{DO}
				\item[] \{
				\item[] 	Solve equations
				\item[]    $\sum_{x,y}\widetilde{p}(x)p(y|x)f_i(x,y)e^{\delta_i\sum_{i=1}^{n}f_i(x,y)} = \widetilde{p}(f_i)$
				\item[] Let $\lambda_i := \lambda_i + \delta_i$
				\item[] \}
			\end{itemize}
			\item[Step3] Check convergence.
		\end{itemize}
	\end{frame}

	\section{Distance and Divergence}
	\begin{frame}
		\frametitle{Distance}
		\textbf{Distance} satisfies four constraints which \text{Divergence} may no satisfy.
		\begin{itemize}
			\item \textbf{Non-negativity:} $\forall x,y,\quad d(x,y) \ge 0$
			\item \textbf{Non-degeneracy:} $d(x,y)=0 \Leftrightarrow x=y$
			\item \textbf{Symmetry:} $\forall x,y, \quad d(x,y)=d(y,x)$
			\item \textbf{Triangularity:} $\forall x,y,z \quad d(x,z)\leq d(x,y)+d(y,z)$
		\end{itemize}
		\begin{figure}
			\pgfimage[width=4cm]{"image/29.png"}
		\end{figure}

@@

	\begin{frame}
		\frametitle{Distance(3)}
		\textbf{Why is Euclidean distance not a good metric in most situation?}
		\begin{itemize}
			\item Vector length often is not determinant.
			\item Most Problems are in high-dimensional.
			\item Most of the volume of a high-dimensional orange is in the skin, not the pulp.
		\end{itemize}
		\begin{figure}
			\pgfimage[width=3cm ]{"image/30.png"}
		\end{figure}
	\end{frame}

	\begin{frame}
		\frametitle{Divergence}
	\end{frame}
\end{document}
